\documentclass[a4paper, draft]{article}

\author{Pin-Hsuan Tseng, Arun Muthu}
\title{Scope of Work: Unipark Bay Booking System}

\begin{document}
\maketitle

\subsection*{Preface}
This document addresses the requirements of the Unipark bay booking system.
The intended audience for this document are the designers and the clients of the project.

\subsection*{Team Members}
Arun Muthu, Dylan Kennedy, Jayden Teo, Joel Fitzpatrick, Joel Milligan, Pin-Hsuan Tseng

\section{Introduction}
The current system used by UWA departments to book parking bays for
VIP guests requires booking requests via email and data storage in
Excel spreadsheets. This project aims to address the inefficiencies
of the process by creating an online calendar booking system where
customers can see car parks and bays available, in a similar fashion
to the UWA Library booking system. Unipark admin will then be able
to view and approve requests on the website.

\section{Deliverables}
\begin{itemize}
    \item [2.0.0] A desktop website deployed on a cloud service such as Heroku.
          The website will be publicly accessible
    \item [2.1.0] Skills/Resources Audit
    \item [2.2.0] Project Acceptance Tests
    \item [2.3.0] Risk Register
    \item [2.4.0] User stories
    \item [2.5.0] User documentation on how to navigate and use the site
    \item [2.6.0] Minutes of the Client Project Retrospective
\end{itemize}

\section{Requirements}
\begin{itemize}
    \item [3.0.0] Desktop support only
    \item [3.1.0] Users will be able to select a date (next day onward) and a carpark
          (5 total as of now) before choosing a specific bay and timeslot.
          \begin{itemize}
              \item When a car bay timeslot is selected, the system will
                    automatically book the 30-minute time slot before and after
                    as a buffer system.
              \item If the 30-minute timeslot is already booked, it will do nothing.
                    This creates a 15-minute buffer between bay bookings.
          \end{itemize}
    \item [3.1.1] Users may book several bays (within the same day) in one booking.
    \item [3.1.2] Users will need to enter specific details such as name, email address,
          phone number and optionally their company and car registration number
          to confirm the booking request.
    \item [3.2.0] Admin staff will receive an email linking to the booking request page when
          a new booking request is submitted.
    \item [3.2.1] After an admin approves the booking request, an email will be automatically
          sent to the user and all admin staff containing an A3 printable PDF summary
          of the booking.
    \item [3.2.2] Admin staff will have access to the following functionality in the admin panel:
          \begin{itemize}
              \item View, approve, or decline booking requests.
              \item Create, edit or delete car parks.
                    Each car park has a name with optional description and link to a location on Google Maps.
              \item Create, edit or delete bays within car parks.
                    Each bay has a number and optional description.
              \item Add, edit or delete admin accounts.
                    Each admin account has a username and password which can be modified.
              \item Edit website settings including a contact number (displayed on the starting page)
                    and the start and end time for booking parking bays.
              \item Block or unblock requests from particular emails.
          \end{itemize}
    \item [3.3.0] A help button (e.g. question mark) will be available in the corner of each page to assist users.
\end{itemize}

\end{document}
